\textsf{Are large language models superhuman chemists?}

### 2024-10-30 src/tex/appendix.tex
fix: add flattened pdfs

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/CB_HUMANSET_FIG_V2-flat.pdf}
    \caption{\textbf{Composition of the human subset.} The circular plot shows the distribution of topics and required skills in the human subset of the \chembench corpus. The human subset is a representative subset of the full corpus, with a balanced distribution of topics and skills.}
    \label{fig:cb_humanset}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/CB_SKILL_FIG_V1.pdf}
    \caption{\textbf{Composition of the required skills considered in the \chembench corpus.} The circular plot shows the distribution of required skills in the \chembench corpus.}
    \label{fig:cb_skillset}
\end{figure}

\begin{xltabular}{\textwidth}{X}

@@

    \caption{\textbf{Examples for each of the required skills considered in the \chembench corpus.} The table shows the number of questions for each skill and an example question. Note that the total count in this table is bigger than the \chembench corpus. This is because the same question can be annotated with two different \enquote{requires} skills, i.e. Reasoning and Calculation.} \\

@@

\end{xltabular}

@@

\begin{figure}[htb]
    \centering
    \includegraphics[width=\textwidth]{figures/corpus_human_comparison.pdf}
    \caption{\textbf{
        Performance of the models on the \chembench corpus and \chembenchmini subset.} The bar plot shows the fraction of questions that were answered completely correctly, highlighting the relative performance of different models on both the \chembench corpus and the \chembenchmini subset.
        We see that the model ranking remains fairly consistent across both sets}
    \label{fig:performance_corpus_and_tiny}
    \script{corpus_humanset_performance.py}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/CB_HUMANSET_FIG_V2.pdf}
    \caption{\textbf{Composition of the human subset.} The circular plot shows the distribution of topics and required skills in the human subset of the \chembench corpus. The human subset is a representative subset of the full corpus, with a balanced distribution of topics and skills.}
    \label{fig:cb_humanset}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/CB_SKILL_FIG_V2.pdf}
    \caption{\textbf{Composition of the required skills considered in the \chembench corpus.} The circular plot shows the distribution of required skills in the \chembench corpus.}
    \label{fig:cb_skillset}
\end{figure}

@@

    \caption{\textbf{Examples for each of the required skills considered in the \chembench corpus.} The table shows the number of questions for each skill and an example question. Note that the total count in this table is bigger than the \chembench corpus. This is because the same question can be annotated with two different \enquote{requires} skills, i.e. Reasoning and Calculation.}

@@

In analyzing the performance of state-of-the-art models on the \chembench corpus, we identified several chemical topics where the models consistently struggled to provide correct answers. \Cref{tab:chembench_corpus_models_failed_topic} presents examples of challenging questions across different chemical domains, highlighting specific areas where current models need improvement

\begin{table}
    \centering
    \small
    \caption{\textbf{Examples of some questions failed for all the state-of-the-art models.} The table shows examples of the \chembench corpus for which all models considered in \Cref{fig:human_vs_models_bar} fail to answer correctly.}
    \label{tab:chembench_corpus_cognitive}
    {\fontsize{8}{9}\selectfont
        \begin{tabularx}{\textwidth}{X}
            \toprule
            Which of the following compounds are capable of producing hazardous explosive peroxides? \\
            A. Cyclohexene \\
            B. Cyclooctene \\
            C. Decalin \\
            D. Ethyl ether \\
            E. Isopropyl ether \\
            F. Para-dioxane \\
            G. Tetralin \\
            \midrule
            What is the oxidation number of hydrogen in the reactants of Sabatier reaction? \\
            \midrule
            How does a non-competitive inhibitor influence the enzyme kinetics of a reaction in the Lineweaver-Burk-plot when compared to a competitive inhibitor? \\
            A. The intersection with y-axis shift to higher numbers \\
            B. The intersection with y-axis shift to lower numbers \\
            C. The slope decreases \\
            D. The slope increases \\
            \midrule
            Poly(lactic acid) (PLA) can be broken down enzymatically to lactic acid monomer and compound B (a dimer of lactic acid). A plastic sample degraded to 1.044 g, and titration showed it needed \SI{19.40}{cm^{3}} of \SI{0.100}{mol dm^{-3}} \ce{NaOH} to neutralize. What is the number of moles of acid in the sample? \\
            \midrule
            What is hydrofluoric acid used for? \\
            A. For cleaning facades \\
            B. For etching glass \\
            C. For filling accumulators \\
            D. For soldering \\
            \midrule
            How many chiral centers are present in the molecular structure of citric acid? \\
            \midrule
            What is the sum of the stoichiometric coefficients on the left side of the redox reaction equation: \ce{Cd(NCS)2 + KNO3 -> K2CO3 + CO + SO2 + N2 + CdO}? \\
            A. 10 \\
            B. 14 \\
            C. 18 \\
            D. 23 \\
            E. 9 \\
            \midrule
            The ligand-field splitting energy (LFSE) is computed as $LFSE=-0.4\cdot Dq \cdot n+0.6 \cdot Dq \cdot m$ with $n$ being the number of electrons in t2g d orbitals ($\mathrm{d}_{xz}$, $\mathrm{d}_{yz}$ and $\mathrm{d}_{xy}$), $m$ the number of electrons in eg d orbitals ($\mathrm{d}_{x^2-y^2}$ and $\mathrm{d_{z^2}}$), and Dq the ligand field splitting parameter. What is the value of LFSE in terms of Dq for the low-spin case in the metal complex tetramethylamine diaquacopper(II) ion? \\
            \midrule
            In phenol's mass spectrum, how does the intensity of the m/z 95 peak compare to the molecular ion peak at m/z 94? \\
            A. 10.0\% \\
            B. 6.6\% \\
            C. 7.0\% \\
            D. 94\% \\
            \bottomrule
        \end{tabularx}
    }
\end{table}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/corpus_human_comparison.pdf}
    \caption{\textbf{
        Performance of the models on the \chembench corpus and \chembenchmini subset.} The bar plot shows the fraction of questions that were answered completely correctly, highlighting the relative performance of different models on both the \chembench corpus and the \chembenchmini subset.
        We see that the model ranking remains fairly consistent across both sets}
    \label{fig:performance_corpus_and_tiny}
    \script{corpus_humanset_performance.py}
\end{figure}

\begin{table}
    \caption{\textbf{Performance of the models on the \chembench corpus.} The table shows the fraction of questions answered completely correctly by the models for different skills and difficulty levels.}
    \resizebox{\textwidth}{!}{
    \variable{output/performance_table.tex}
    }
    \label{tab:performance_table}
\end{table}

\begin{table}
    \caption{\textbf{Performance of the models on \chembenchmini.} The table shows the fraction of questions answered completely correctly by the models for different skills and difficulty levels.}
    \resizebox{\textwidth}{!}{
    \variable{output/performance_table_human_subset.tex}
    }
    \label{tab:performance_table_human_subset}
\end{table}
